Forecasting the age structure of the scientific workforce in Australia

### 2025-09-23 age_structure_forecasts.qmd
Updated yaml for new templates

---
title: "Forecasting the age structure of the scientific workforce in Australia"
author:
- name: Rob J Hyndman
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton
      country: Australia
      postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Khuyen Vanh Nguyen
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton VIC
      country: Australia
      postal-code: 3800
abstract: |
  Planning for a future workforce requires forecasts of age structure changes to inform policy decisions, particularly related to universities and immigration. We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modelling exits through death and retirement, and including a remainder term that captures migration and career changes. Functional data models are used to model age-specific components, while ARIMA models are used for time series components. Simulation is employed to generate forecast distributions, capturing uncertainty from all components. The approach is illustrated using data on Australia's scientific workforce, allowing us to forecast the age distribution of various scientific disciplines for the next ten years. This analysis was central to an Australian Academy of Science initiative examining the capability of Australia's science system and identifying workforce gaps.
keywords:
  - cohort analysis
  - demographic modelling
  - functional data models
  - labour market
  - workforce planning
bibliography: refs.bib
wpnumber: no/yr
jelcodes: J11, J21, C15, C22
blind: false
cover: true
linestretch: 1.5
include-in-header: preamble.tex
format:
  wp-pdf:
    keep-tex: true
filters:
  - blindable-div
---

@@

# Acknowledgements {-}

We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report.

>>>>

---
title: "Forecasting the age structure of the scientific workforce in Australia"
shorttitle: "Forecasting the workforce age structure"
author:
- name: Rob J Hyndman
  affiliation:
    - ref: ebs
  email: Rob.Hyndman@monash.edu
  corresponding: true
  orcid: 0000-0002-2140-5352
- name: Khuyen Vanh&nbsp;Nguyen
  affiliation:
    - ref: ebs
affiliations:
    - id: ebs
      name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton
      country: Australia
      postal-code: 3800
abstract: |
  Planning for a future workforce requires forecasts of age structure changes to inform policy decisions, particularly related to universities and immigration. We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modelling exits through death and retirement, and including a remainder term that captures migration and career changes. Functional data models are used to model age-specific components, while ARIMA models are used for time series components. Simulation is employed to generate forecast distributions, capturing uncertainty from all components. The approach is illustrated using data on Australia's scientific workforce, allowing us to forecast the age distribution of various scientific disciplines for the next ten years. This analysis was central to an Australian Academy of Science initiative examining the capability of Australia's science system and identifying workforce gaps.
keywords:
  - cohort analysis
  - demographic modelling
  - functional data models
  - labour market
  - workforce planning
acknowledgement: |
  We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report. Rob Hyndman is a member of the Australian Research Council Industrial Transformation Training Centre in Optimisation Technologies, Integrated Methodologies, and Applications (OPTIMA), Project ID IC200100009. He also receives funding from the Australian Research Council through Discovery Project DP250100702.
bibliography: refs.bib
wpnumber: no/yr
jelcodes: J11, J21, C15, C22
blind: false
cover: true
linestretch: 1.5
include-in-header: preamble.tex
format:
  wp-pdf+wp: default
  quarto-anzjs-pdf:
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
filters:
  - blindable-div
---

@@
